Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-02-06 Documents/Euler/Benchmarks1D/draft.tex
zoomed density for test 9
captions 2-8

\altaffiltext{1}{Insert Juliana's affiliation and email}
\altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=.78\textwidth]{den128comp_20}
  \end{center}
  \caption{density}
\end{figure}
%\newpage

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs128comp_20} &
	  \includegraphics[width=.425\textwidth]{vel128comp_20}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

@@

\subsection{Test 2}
For subsequent tests, the number of cells was consistent within each test, and the integration method was varied as in the first test. 
The graphs for the second test show a result common throughout many of the different tests: The first order integration method is considerably far from the exact solution; the second and third order integration methods yield nearly identical results which are near, but not exactly equal to, the exact solution. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T2.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T2.png} &
	  \includegraphics[width=.425\textwidth]{vel_T2.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

@@

\subsection{Test 3}
Test 3 shows results similar to Test 2. The deviation of experimental results from exact is especially noticeable in velocity. Near the initial point of discontinuity, the exact results appear completely horizontal. Method 1 almost completely ignores this horizontal part, while Methods 2 and 3 smooth it out considerably. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T3.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T3.png} &
	  \includegraphics[width=.425\textwidth]{vel_T3.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T4.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T4.png} &
	  \includegraphics[width=.425\textwidth]{vel_T4.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T5.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T5.png} &
	  \includegraphics[width=.425\textwidth]{vel_T5.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}
\clearpage

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T6.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T6.png} &
	  \includegraphics[width=.425\textwidth]{vel_T6.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T7.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T7.png} &
	  \includegraphics[width=.425\textwidth]{vel_T7.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T8.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T8.png} &
	  \includegraphics[width=.425\textwidth]{vel_T8.png}
	\end{tabular}
  \end{center}
  \caption{pressure and velocity}
\end{figure}

@@

%\begin{figure}[h]
 % \begin{center}
	%\begin{tabular}{cc}
     % \includegraphics[width=.4\textwidth]{den_T9.png} &
	  %\includegraphics[width=.4\textwidth]{denT9zoom.png} \\
	  %\includegraphics[width=.4\textwidth]{prs_T9.png} &	
      %\includegraphics[width=.4\textwidth]{vel_T9.png}\\
	%\end{tabular}	
  %\end{center}
 % \caption{}
%\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T9.png}	
  \end{center}
  \caption{density}
\end{figure}

\begin{figure}
  \begin{center}
     \includegraphics[width=.78\textwidth]{prs_T9.png}	
  \end{center}
  \caption{pressure}
\end{figure}

\begin{figure}
  \begin{center}
     \includegraphics[width=.78\textwidth]{vel_T9.png}	
  \end{center}
  \caption{velocity}
\end{figure}
\clearpage

>>>>

\altaffiltext{1}{Bearden High School, Knoxville, TN 37919-5449, USA}
\altaffiltext{2}{Computational and Applied Mathematics Group, Oak Ridge National Laboratory, Oak Ridge, TN 37831-6354, USA; endevee@ornl.gov}

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=.78\textwidth]{den128comp_20}
  \end{center}
  \caption{Results showing the density for Sod's shock tube at $t=0.2$, computed with 128 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den128comp}
\end{figure}
%\newpage

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs128comp_20} &
	  \includegraphics[width=.425\textwidth]{vel128comp_20}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den128comp}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\subsection{Test 2}
For subsequent tests, the number of cells was consistent within each test, and the integration method was varied as in the first test. 
The graphs for the second test show a result common throughout many of the different tests: The first order integration method is considerably far from the exact solution; the second and third order integration methods yield nearly identical results which are near, but not exactly equal to, the exact solution. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T2.png}	
  \end{center}
  \caption{Results showing the density for test 2 at $t=0.2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T2}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T2.png} &
	  \includegraphics[width=.425\textwidth]{vel_T2.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T2}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\subsection{Test 3}
Test 3 shows results similar to Test 2. The deviation of experimental results from exact is especially noticeable in velocity. Near the initial point of discontinuity, the exact results appear completely horizontal. Method 1 almost completely ignores this horizontal part, while Methods 2 and 3 smooth it out considerably. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T3.png}	
  \end{center}
  \caption{Results showing the density for test 3 at $t=0.15$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T3}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T3.png} &
	  \includegraphics[width=.425\textwidth]{vel_T3.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T3}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T4.png}	
  \end{center}
  \caption{Results showing the density for test 4 at $t=1$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T4}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T4.png} &
	  \includegraphics[width=.425\textwidth]{vel_T4.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T4}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T5.png}	
  \end{center}
  \caption{Results showing the density for test 5 at $t=0.012$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T5}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T5.png} &
	  \includegraphics[width=.425\textwidth]{vel_T5.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T5}:
  velocity (left panel) and pressure (right panel).}
\end{figure}
\clearpage

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T6.png}	
  \end{center}
  \caption{Results showing the density for test 6 at $t=0.035$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T6}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T6.png} &
	  \includegraphics[width=.425\textwidth]{vel_T6.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T6}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T7.png}	
  \end{center}
  \caption{Results showing the density for test 7 at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T7}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T7.png} &
	  \includegraphics[width=.425\textwidth]{vel_T7.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T7}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T8.png}	
  \end{center}
  \caption{Results showing the density for test 8 at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T8}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{prs_T8.png} &
	  \includegraphics[width=.425\textwidth]{vel_T8.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T8}:
  velocity (left panel) and pressure (right panel).}}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.4\textwidth]{den_T9.png} &
	  \includegraphics[width=.4\textwidth]{denT9zoom.png} \\
	  \includegraphics[width=.4\textwidth]{prs_T9.png} &	
      \includegraphics[width=.4\textwidth]{vel_T9.png}\\
	\end{tabular}	
  \end{center}
  \caption{}
\end{figure}
